### 2013-05-02 paper/tex/performance.tex
experiment done.

Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{}.

>>>>

Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{tab:redis}. Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has $25316.46$ and $17421.60$ throughput respectively.

\begin{table}
\centering
\caption{Redis Server Benchmark}
\begin{tabular}{ll}\toprule
Redis Operations & Benchmark Results \\\midrule
PING & 26109.66 requests per second \\
MSET & 12406.95 requests per second \\
SET & 17421.60 requests per second \\
GET & 25316.46 requests per second \\
INCR & 24813.90 requests per second \\
LPUSH & 27700.83 requests per second \\
LPOP & 28169.02 requests per second \\
SADD & 28169.02 requests per second \\
SPOP & 27777.78 requests per second \\
LPUSH & 27855.15 requests per second \\
LRANGE & 3373.82 requests per second \\\bottomrule
\end{tabular}
\label{tab:redis}
\end{table}
